# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

Download the zip from the web into a temporary folder on your local device. Once
done, unzip the file and read the data into a data frame.

Once data has been read, remove all the NA values from the data frame

```{r echo = TRUE}
library(RCurl)
setInternet2(TRUE) 
forecasturl <- paste("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip")
td <- tempdir()
tf <- tempfile(tmpdir=td, fileext=".zip")
download.file(forecasturl, tf)
fname <- unzip(tf, list=TRUE)$Name[1]
unzip(tf, files=fname, exdir=td, overwrite=TRUE)
fpath <- file.path(td, fname)
MDataNA <- read.csv(fpath)
MData <- na.omit(MDataNA)

```


## What is mean total number of steps taken per day?

Make a histogram of the total number of steps taken each day

Calculate and report the mean and median total number of steps taken per day


```{r echo = TRUE}
MData$date <- as.Date(as.character(MData$date))
MData$steps <- as.numeric(MData$steps)

MData2 <- MData

MData2 <- aggregate(MData2$steps, list(MData2$date), sum)

install.packages("plotrix")
library("plotrix")
barp(MData2$x)

sapply(split(MData$steps, MData$date), mean)

sapply(split(MData$steps, MData$date), median)

```




## What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

Find the 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps.

```{r echo = TRUE}

DailyActivity <- sapply(split(MData$steps, MData$interval), mean)
plot(DailyActivity)
max(DailyActivity)


```


## Inputing missing values

Calculate the number of missing values
``` {r echo = TRUE}
sum(is.na(MDataNA$steps))

```

Now fill in all the missing values with mean for that particular day
``` {r echo = TRUE}

MDataMod <- MDataNA
MDataMod[is.na(MDataMod)] <- 0

MeanAgg <- aggregate(MDataMod$steps, by=list(MDataMod$date), FUN=mean)


 j <- 1

for (i in 1:61){
     while(MeanAgg$Group.1[i]==MDataNA$date[j] && j <= 17568){
         MDataNA$steps[j]=replace(MDataNA$steps[j],is.na(MDataNA$steps[j]),MeanAgg$x[i])
         j <- j+1
     }
 }


```
Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.

```{r echo = TRUE}
MDataNA$date <- as.Date(as.character(MDataNA$date))
MDataNA$steps <- as.numeric(MDataNA$steps)

MDataNA2 <- MDataNA

MDataNA2 <- aggregate(MDataNA2$steps, list(MDataNA2$date), sum)

install.packages("plotrix")
library("plotrix")
barp(MDataNA2$x)

sapply(split(MDataNA$steps, MDataNA$date), mean)

sapply(split(MDataNA$steps, MDataNA$date), median)

```



## Are there differences in activity patterns between weekdays and weekends?

```{r echo = TRUE}

MDataNA$day <- weekdays(as.Date(MDataNA$date))


for (i in 1:17568){
if (MDataNA$day[i] == "Sunday" || MDataNA$day[i] == "Saturday")
MDataNA$day[i] <- "Weekend"
else
MDataNA$day[i] <- "Weekday"
}

library(ggplot2)

qplot(steps,interval,data=MDataNA, facets=.~day, type=1)

```
